---
title: '6060 Practice: RMarkdown'
author: "Parco Sin"
output:
  pdf_document:
    number_sections: yes
    toc_depth: 3
  html_document:
    toc_depth: '3'
  word_document:
    toc_depth: '3'
---

```{r,echo=FALSE,message=FALSE, warning=FALSE}
# load libraries
library(tidyverse)
library(psych)
library(haven)
library(apaTables)
library(dplyr)

#Load data 
analytic_data <- read_csv("quiz2_analytic_data_female.csv")

```

# Relations among variables for women

Below are the correlations among the variables for all participants (men and women).
Note you will need to use just women in your rmarkdown document.


```{r, echo=FALSE, message=FALSE, warning=FALSE}
psych::pairs.panels(analytic_data)        
```

\pagebreak

# Distributions
## Distributions of negative affect scores

Below we can see the distribution of negative affect scores is skewed.

```{r,echo=FALSE,message=FALSE, warning=FALSE}
my.hist2 <- ggplot(analytic_data,aes(neg_affect))
my.hist2 <- my.hist2 + geom_histogram(aes(y= ..count..), binwidth=1, fill="black", color="black")
my.hist2 <- my.hist2 + labs(title="Negative Affect Score",x="Negative Affect", y="Frequency")
my.hist2 <- my.hist2 + theme_classic()
my.hist2 <- my.hist2 + theme(axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
                           axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))
my.hist2 <- my.hist2 + scale_x_continuous( breaks = seq(0, 3,by=0.5) )
my.hist2 <- my.hist2 + scale_y_continuous( breaks = seq(0,1600,by=400), expand=c(0,0) )
ggsave("Figure_5_NegativeAffect_Histogram_Female.tiff", plot=my.hist2, width=6,height=6)
print(my.hist2)
```

\pagebreak

## Neuroticism Distribution

Below we can see the distribution of neuroticism scores is relatively normal.

```{r,echo=FALSE,message=FALSE, warning=FALSE}
my.hist <- ggplot(analytic_data,aes(Neuroticism))
my.hist <- my.hist + geom_histogram(aes(y= ..count..), binwidth=1, fill="black", color="black")
my.hist <- my.hist + labs(title="Neuroticism Score",x="Neuroticism", y="Frequency")
my.hist <- my.hist + theme_classic()
my.hist <- my.hist + theme(axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
                           axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))
my.hist <- my.hist + scale_x_continuous( breaks = seq(0,25,by=5) )
my.hist <- my.hist + scale_y_continuous( breaks = seq(0,150,by=10), expand=c(0,0) )
ggsave("Figure_4_Neuroticism_Histogram_Female.tiff", plot=my.hist, width=6,height=6)
print(my.hist)

```

\pagebreak

#Relations among variables
##Scatter plot for Negative Affect and Neuroticism

Below you can see the correlation between negative affect and neuroticism with a regression line.

```{r,echo=FALSE,message=FALSE, warning=FALSE}
my.plot <- qplot(neg_affect, Neuroticism, data=analytic_data)
my.plot <- my.plot + geom_smooth(method = "lm" , se = FALSE, color = "black")
my.plot <- my.plot + theme_classic(14)
my.plot <- my.plot + theme(axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
                           axis.line.y = element_line(colour = 'black', size=0.5, linetype = 'solid'))
my.plot <- my.plot + labs(title="", x="Negative Affect", y="Neuroticism")
my.plot <- my.plot + coord_cartesian(xlim=c(0,3), ylim=c(0,25))

print(my.plot)
```

